Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-19 EconGrowth.Rnw
Changed order of confidence intervals in tables.

# Now create the data for a table.
dataCD <- rbind(lowerCD, estCD, upperCD); dataCD
colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCD <- xtable(dataCD, caption="U.S. Cobb-Douglas, 1980-2011", digit = c(4, 4, 2, 2, 1))
@

@@

  # Now create the data for a table.
  dataCDe <- rbind(lowerCDe, estCDe, upperCDe)
  print(dataCDe)

>>>>

# Now create the data for a table.
dataCD <- rbind(upperCD, estCD, lowerCD); dataCD
colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCD <- xtable(dataCD, caption="U.S. Cobb-Douglas, 1980-2011", digit = c(4, 4, 2, 2, 1))
@

@@

  # Now create the data for a table.
  dataCDe <- rbind(upperCDe, estCDe, lowerCDe)
  print(dataCDe)
